### 2013-04-26 inst/examples/BUGS/allen.Rmd
parametric bayes initialized with true parameter values still performs poorly.

```{r}
  posteriors_plot(gp, priors) # needs trace=TRUE!
```

@@

```{r}
library(emdbook)
library(coda)
tfit_jags_m <- as.mcmc.bugs(jagsfit$BUGSoutput)
print(xyplot(tfit_jags_m))
print(densityplot(tfit_jags_m))
```

>>>>

```{r}
hyperparameters <- c("index", "s2", "tau2", "beta0", "nug", "d", "ldetK")
posteriors <- melt(gp$trace$XX[[1]][,hyperparameters], id="index")
ggplot(posteriors) + geom_line(aes(index, value)) + facet_wrap(~ variable, scale="free")

prior_curves <- ddply(posteriors, "variable", function(dd){
    grid <- seq(min(dd$value), max(dd$value), length = 100)
    data.frame(value = grid, density = priors[[dd$variable[1]]](grid))
})

ggplot(posteriors) + geom_histogram(aes(x=value, y=..density..), alpha=0.7) +
    geom_line(data=prior_curves, aes(x=value, y=density), col="red", lwd=2) +
    facet_wrap(~ variable, scale="free")
```

@@

```{r}
library(emdbook)
library(coda)
tfit_jags_m <- as.mcmc.bugs(jagsfit$BUGSoutput)
print(xyplot(tfit_jags_m))
print(densityplot(tfit_jags_m))

par_posteriors <- as.data.frame(tfit_jags_m)
```
